Poincar\'e--Friedrichs constants over triangulated domains

### 2024-06-20 main.tex
Update on Overleaf.

@@

    Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $\nabla w_{m-1} = \nabla u$ over $\Omega_m$. Hence $c_{\star} := w_{m-1} - u_{|\Omega_{m-1}}$ is a constant. 
    By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j(m)}$.

    Let $\hat T$ be the reference simplex.
    We fix affine homeomorphisms $\Phi_1 : \hat T \rightarrow T_1$ and $\Phi_2 : \hat T \rightarrow T_2$
    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
    Note that these affine transformations define a bi-Lipschitz mapping $\Phi : \hat U \rightarrow U$.

    We define $u'_{m+1} := u_{{m}} \circ \Phi_1 \circ \Phi_2^{-1} \in W^{1,p}(T_{m+1})$. 
    In particular, $u'_{m+1} \in W^{1,p}(T_{m+1})$ such that 
    \begin{align*}
        \trace_F u_{m} = \trace_F u'_{m+1}
    \end{align*}
    We will also use the bound 
    \begin{align*}
        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
        &\leq 
        |\det(\Dif \Phi_1)|^{-\frac 1 p} \cdot \| \Dif \Phi_1 \|
        \cdot 
        |\det(\Dif \Phi_2)|^{-\frac 1 p} \cdot \| \Dif \Phi_2 \|
        \| \nabla u_{m} \|_{L^{p}(T_{m})}
        .
    \end{align*}
    Suppose that $u''_{m+1} \in W^{1,p}(T_{m+1})$ with 
    \begin{align*}
        \nabla u''_{m+1} = \nabla u - \nabla u'_{m+1}, 
        \quad 
        \trace_{F_{m}} u''_{m+1} = 0
    \end{align*}
    Such $u''_{m+1}$ exists because 
    \begin{align*}
        \trace_{F_{m}}( \nabla u - \nabla u'_{m+1} ) 
        &= 
        \trace_{F_{m}} \nabla u - \trace_{F_{m}} \nabla u'_{m+1}
        \\&= 
        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} u'_{m+1}
        = 
        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} u_{|m}
        = 0
        .
    \end{align*}
    Setting $u_{m+1} = u_{m}$ over $\Omega_{m}$ and $u_{m+1} = u'_{m+1} + u''_{m+1}$ over $T_{m+1}$, 
    we find 
    \begin{gather*}
        \nabla u_{m+1} = \nabla u'_{m+1} + \nabla u''_{m+1} = \nabla u'_{m+1} + \nabla u - \nabla u'_{m+1} = \nabla u,
        % \end{gather*}
        \\
        % \begin{gather*}
        \trace_{F_{m}} u_{m+1} = \trace_{F_{m}} u'_{m+1} = \trace_{F_{m}} u_1.
    \end{gather*}
    We construct such a $u''_{m+1} \in W^{1,p}(T_{m+1})$ satisfying desirable bounds.
    There exists $\Psi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
    We define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \Psi - u'_{m+1} \circ \Psi )$. 
    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$,
    and extend that $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
    By construction, $\hat g$ is the gradient of a unique function in $w \in W^{1,p}$ that vanishes at the boundary of $\hat U$,
    which satisfies Friedrichs inequality. In total, we utilize 
    \begin{gather*}
        \| u''_{m+1} \|_{L^{p}(T_{m+1})}
        \leq 
        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
        \| w \|_{L^{p}(\hat T)}
        ,
        \qquad 
        \| w \|_{L^{p}(\hat U)} 
        \leq 
        2 
        \| \hat g \|_{\bfL^{p}(\hat U)}
        ,
        \\
        \| \hat g \|_{\bfL^{p}(\hat U)}
        \leq 
        2^{\frac n p}
        \| \hat g \|_{\bfL^{p}(\hat T)}
        \leq 
        2^{\frac n p}
        |\det(\Dif \Psi_1)|^{-\frac 1 p} \cdot \| \Dif \Psi_1 \|
        \| \nabla u - \nabla u'_{m+1} \|_{\bfL^{p}(T)}
        .
    \end{gather*}
    We thus have
    \begin{align*}
        \| u''_{m+1} \|_{L^{p}(T_{m+1})}
        &
        \leq 
        \| \nabla u \|_{L^{p}(T_{m+1})} 
        + 
        2^{1+\frac n p}
        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
        \\&
        \leq 
        \| \nabla u \|_{L^{p}(T_{m+1})} 
        + 
        2^{1+\frac n p}
        \| \Dif \Psi \|
        \| \Dif \Psi \|
        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
        .
    \end{align*}

>>>>

Upper bound for the classical Poincar\'e inequality over a simplex is easily found. 
We can use it to compute an upper bound for the Poincar\'e--Friedrichs inequality 
when homogeneous boundary conditions are imposed on a single face of the boundary.

\begin{lemma}
    Let $T$ be an $n$-simplex and with a face $F$. 
    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
    \begin{align*}
        \| u \|_{L^{p}(T)}
        &
        \leq 
        C_{\partial,p}
        \diam(T) \| \nabla u \|_{L^{p}(T)}
    \end{align*}
    where 
    \begin{align*}
        C_{\partial,p}
        \leq 
        \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right) 
        .
    \end{align*}
    % \begin{align*}
    %     \| u \|_{L^{p}(T)}
    %     &
    %     \leq 
    %     C_{?} \diam(T)
    %     \| \nabla w \|_{\bfL^{p}(T)}
    %     +
    %     \| \gamma \|_{\bfL^{p}(T)}
    %     \\&
    %     \leq 
    %     C_{?} \diam(T)
    %     \| \nabla u \|_{\bfL^{p}(T)}
    %     +
    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
    %     \diam(T)
    %     \| \nabla w \|_{L^{p}(T)}
    %     \\&
    %     \leq 
    %     C_{?} 
    %     \diam(T) \| \nabla u \|_{\bfL^{p}(T)}
    %     +
    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
    %     \\&
    %     \leq 
    %     \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right) 
    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
    %     .
    % \end{align*}
\end{lemma}
\begin{proof}
    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
    \[
        \| w \|_{L^{p}(T)}
        \leq 
        C_{?}
        \| \nabla w \|_{\bfL^{p}(T)}
        .
    \]
    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
    We use that 
    \[
        \| \gamma \|_{L^{p}(T)}
        =
        \gamma \vol(T)^\frac{1}{p}
        =
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \cdot 
        \gamma 
        \vol(F)^\frac{1}{p}
        \leq 
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \| \gamma \|_{L^{p}(F)}
        .
    \]
    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
    \begin{align*}
        \| \gamma \|_{L^{p}(F)}^{p}
        &
        \leq 
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p}
        +
        p
        \cdot 
        \diam(T)
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p-1}
        \| \nabla w \|_{L^{p}(T)}
        \\&
        \leq 
        \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right) 
        \diam(T)^{p}
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \| \nabla w \|_{L^{p}(T)}^{p}
        .
    \end{align*}
    Recall that $u = w - \gamma$. The desired result follows. 
\end{proof}

@@

    First, there exists $w_0 \in W^{1,p}(T_{0})$ such that $\nabla w_{0} = \nabla u$ over $\Omega_0$. 
    Suppose that $0 \leq m < M$ such that there exists $w_{m} \in W^{1,p}(\Omega_{m})$ with $\nabla w_{m} = \nabla u$ over $\Omega_m$. 
    Hence $w_{m} - u_{|\Omega_{m}}$ is a constant.

    By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j(m)}$. 
    Let $\hat T$ be the reference simplex.
    We fix affine homeomorphisms $\Phi : \hat T \rightarrow T_{j(m)}$ and $\Theta : \hat T \rightarrow T_{m+1}$,
    each of which maps the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
    We define $w'_{m+1} := w_{{m}} \circ \Phi \circ \Theta^{-1} \in W^{1,p}(T_{m+1})$. 
    %
    {\color{blue}We define $w'_{m+1} := w_{m} \circ \Xi \in W^{1,p}(T_{m+1})$,
    where $\Xi : T_{m+1} \rightarrow T_{j(m)}$ is the unique affine homeomorphism that leaves $F$ invariant. }
    %
    By construction, $w'_{m+1} \in W^{1,p}(T_{m+1})$ with 
    \begin{align*}
        \trace_F w_{m} = \trace_F w'_{m+1}
        .
    \end{align*}
    Suppose that $w''_{m+1} = u - w'_{m+1} \in W^{1,p}(T_{m+1})$.
    It satisfies 
    \begin{align*}
        \nabla w''_{m+1} = \nabla u - \nabla w'_{m+1}, 
        \quad 
        \trace_{F_{m}} w''_{m+1} = 0.
    \end{align*}
    The trace condition holds because 
    \begin{align*}
        \trace_{F_{m}}( \nabla u - \nabla w'_{m+1} ) 
        &= 
        \trace_{F_{m}} \nabla u - \trace_{F_{m}} \nabla w'_{m+1}
        \\&= 
        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w'_{m+1}
        = 
        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w_{m}
        = 
        0
        .
    \end{align*}
    Setting $w_{m+1} := w_{m}$ over $\Omega_{m}$ and $w_{m+1} := w'_{m+1} + w''_{m+1}$ over $T_{m+1}$, 
    we find 
    \begin{gather*}
        \nabla w_{m+1} = \nabla w'_{m+1} + \nabla w''_{m+1} = \nabla w'_{m+1} + \nabla u - \nabla w'_{m+1} = \nabla u,
        % \end{gather*}
        \\
        % \begin{gather*}
        \trace_{F_{m}} w_{m+1} = \trace_{F_{m}} w'_{m+1} = \trace_{F_{m}} w_{m}.
    \end{gather*}
    That means that $w_{m+1} \in W^{1,p}(\Omega_{m+1})$ with $\nabla w_{m+1} = \nabla u$ over $\Omega_{m+1}$. 
    As we will show soon, there exists $D_{m+1} > 0$ such that 
    \begin{gather*}
        \| u''_{m+1} \|_{L^{p}(T_{m+1})} 
        \leq 
        D_{m+1} \diam(T_{m+1}) \cdot \| \nabla u - \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}.
    \end{gather*}
    Therefore, 
    \begin{align*}
        \| u''_{m+1} \|_{L^{p}(T_{m+1})}  
        &
        \leq 
        D_{m+1} \diam(T_{m+1}) \| \nabla u        \|_{L^{p}(T_{m+1})} 
        + 
        D_{m+1} \diam(T_{m+1}) \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})} 
        .
    \end{align*}
    We use also the inequality 
    \begin{align*}
        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
        &\leq 
        |\det(\Dif \Phi  )|^{-\frac 1 p} \cdot \| \Dif \Phi   \|
        \cdot 
        |\det(\Dif \Theta)|^{ \frac 1 p} \cdot \| \Dif \Theta^{-1} \|
        \| \nabla u_{m} \|_{L^{p}(T_{m})}
        .
    \end{align*}
    Putting this all together, 
    \begin{align*}
        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
        &\leq 
        \frac{ \vol(T_{m+1})^{\frac 1 p} }{ \vol(T_{m})^{\frac 1 p} } 
        \cdot 
        \| \Dif \Phi   \|
        \cdot 
        \| \Dif \Theta^{-1} \|
        \| \nabla u_{m} \|_{L^{p}(T_{m})}
        .
    \end{align*}
    % TODO: Finish the recursion

    We construct such a $u''_{m+1} \in W^{1,p}(T_{m+1})$ satisfying desirable bounds.
    There exists $\Psi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
    We define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \Psi - u'_{m+1} \circ \Psi )$. 
    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$,
    and extend that $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
    By construction, $\hat g$ is the gradient of a unique function in $w \in W^{1,p}$ that vanishes at the boundary of $\hat U$,
    which satisfies Friedrichs inequality. In total, we utilize 
    \begin{gather*}
        \| u''_{m+1} \|_{L^{p}(T_{m+1})}
        \leq 
        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
        \| w \|_{L^{p}(\hat T)}
        ,
        \qquad 
        \| w \|_{L^{p}(\hat U)} 
        \leq 
        2 
        \| \hat g \|_{\bfL^{p}(\hat U)}
        ,
        \\
        \| \hat g \|_{\bfL^{p}(\hat U)}
        \leq 
        2^{\frac n p}
        \| \hat g \|_{\bfL^{p}(\hat T)}
        \leq 
        2^{\frac n p}
        |\det(\Dif \Psi_1)|^{-\frac 1 p} \cdot \| \Dif \Psi_1 \|
        \| \nabla u - \nabla u'_{m+1} \|_{\bfL^{p}(T)}
        .
    \end{gather*}
    We thus have
    \begin{align*}
        \| u''_{m+1} \|_{L^{p}(T_{m+1})}
        &
        \leq 
        \| \nabla u \|_{L^{p}(T_{m+1})} 
        + 
        2^{1+\frac n p}
        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
        |\det(\Dif \Psi)|^{-\frac 1 p} \cdot \| \Dif \Psi \|
        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
        \\&
        \leq 
        \| \nabla u \|_{L^{p}(T_{m+1})} 
        + 
        2^{1+\frac n p}
        \| \Dif \Psi \|
        \| \Dif \Psi \|
        \| \nabla u'_{m+1} \|_{L^{p}(T_{m+1})}
        .
    \end{align*}
    We will also use the bound.  
\end{proof}
